Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2024-10-11 main.tex
temp

    All algorithms are implemented in C++ and compiled with g++ (v.8.5.0).
    The experiments are managed by simexpal~\cite{DBLP:journals/algorithms/AngrimanGLMNPT19} and executed on workstations with 192 GB RAM and 2x 12-Core Intel Xeon 6126 @3.2 GHz
    and CentOS 8 as OS.
    Code, input data, and experiment scripts are available for review under \skug{\url{insert link}}.

    Next, we describe the set of workflows used in the evaluation and then the clusters on which the
    workflows are scheduled.

    \subsubsection{Workflow instances}
    \skug{Todo: describe the workflows the same asin the abstract}
    We run our experiments on a dataqset comprised of real-world workflows: ones used in~\cite{lotaru} (atacseq, bacass, chipseq,
    eager and methylseq), and ones obtained by increasing their size using the WFGen generator~\cite{COLEMAN202216}.

@@

    Not all tasks have historical runtime data stored in the tables.
    In fact, for two workflows, Bader~\etal do not provide data for more than 50\% of the tasks.
    For two more, around 40\% of tasks have no historical runtime data stored.
    Hence, in the absence of historical data about a task, we give it fixed weights.
    We give it an execution time of $1$, a memory requirement of $50 MB$, and files written and received of $1KB$.
    These values align with the findings of~\cite{lotaru} about small tasks.
%
    \skug{insert more abt how the runtime system hanfles data reads}

    \subsubsection{Target computing systems}
    \skug{Because of the normalized nature of the task/edge weights, I will now be saying that our larger cluster has 192 GB and it
    is represented as 192 000 (with 3 zeroes). For the memory-constrained cluster (192 00 with 2 zeroes) I will say that it has 10 times
    less memory - 19.2 GB. Other processors will be dealt with similarly.}

    To fully benefit from the historical data, the  {\em default} experimental environment
    that we consider is a cluster based on the same six
    kinds of real-world machines that were used in the experimental evaluation in~\cite{lotaru}.
    We set the number of each kind of node to $12$, thus having 72 processors in total. % the whole cluster.

    Each machine has a (normalized) CPU speed and a memory size (in GB), and we list them as (name, speed, memory):
    ($local$, 4, 16) -- very slow machines; ($A1$, 32, 32), ($A2$, 6, 64), ($N1$, 12, 16) -- average machines;
    ($N2$, 8, 8) -- machine with very small memory; and ($C2$, 32, 192) -- {\em luxury} machine with high speed and
    large memory (see Table~\ref{tab:procs}).

    \begin{table}[htb]
        \begin{center}
            \begin{tabular}{rcc}
                \toprule
                Processor name %& Amount
                &  CPU speed (GHz)  &Memory size (GB) \\
                \midrule
                local                    & 4                    & 16     \\
                A1                      & 32                   & 32     \\
                A2                      & 6                    & 64     \\
                N1                      & 12                   & 16     \\
                N2                      & 8                    & 8      \\
                C2                      & 32                   & 192    \\
                \bottomrule
            \end{tabular}
        \end{center}
        \caption{Cluster configuration (default).}
        \label{tab:procs}
    \end{table}

    To more constrained settings, we also vary the cluster configuration and consider
    a memory-constrained cluster.
    Like the default cluster, it consists of 72 nodes (12 of each kind), but we
    give each node $10$ times less memory.
    So, the {\em luxury} machine $C2$ has $19.2$~GB memory in this setting instead of $192$~GB, $A2$ has $6.4$~GB instead
    of $64$~GB etc.
    The processor speeds and their relations stay unchanged.

    \subsubsection{Runtime System}

    To simulate the execution of a workflow, we implemented a runtime system.
    It read the historical data and builds weights for tasks.
    These weights are then treated as the ``truth'' about the execution during the simulation.
    In the case without errors, these values are being sent to the scheduler.
    However, if errors have to be simulated, the runtime system applies a deviation function to the values.
    The deviation function computed a normally distributed deviated value, where the correct value is the mean and the deviation
    is $10\%$.
    This scenario corresponds to the real-life scenarios identified in~\cite{lotaru} and\skug{todo cite someone Jonathan cites}.

>>>>

    All algorithms are implemented in C++ and compiled with g++ (v.8.5.0).
    The experiments are managed by simexpal~\cite{DBLP:journals/algorithms/AngrimanGLMNPT19} and executed on workstations with 192 GB RAM and 2x 12-Core Intel Xeon 6126 @3.2 GHz
    and CentOS 8 as OS.
    Code, input data, and experiment scripts are available to allow reproducibility of results, at~\skug{\url{insert link}}.

    We first describe the set of workflows used for the evaluation, and then the clusters on which the
    workflows are scheduled.

    \subsubsection{Workflow instances}
  %  \skug{Todo: describe the workflows the same asin the abstract}
    We run  experiments on a dataset that consists of real-world workflows: 
    we use workflows coming from~\cite{lotaru} (atacseq, bacass, chipseq,
    eager and methylseq), and also we increase their size using the WFGen generator~\cite{COLEMAN202216}.

@@

    Not all tasks have historical runtime data stored in the tables.
    In fact, for two workflows, Bader~\etal do not provide data for more than 50\% of the tasks.
    For two more, around 40\% of tasks have no historical runtime data stored.
    Hence, in the absence of historical data about a task, we give it fixed weights.
    We give it an execution time of $1$, a memory requirement of $50 MB$, and files written and received of $1KB$.
    These values align with the findings of~\cite{lotaru} about small tasks.
%
 %   \skug{insert more abt how the runtime system hanfles data reads}

    \subsubsection{Target computing systems}
%    \skug{Because of the normalized nature of the task/edge weights, I will now be saying that our larger cluster has 192 GB and it
%    is represented as 192 000 (with 3 zeroes). For the memory-constrained cluster (192 00 with 2 zeroes) I will say that it has 10 times
%    less memory - 19.2 GB. Other processors will be dealt with similarly.}

    To fully benefit from the historical data, the  {\em default} experimental environment
    that we consider is a cluster based on the same six
    kinds of real-world machines that were used in the experimental evaluation in~\cite{lotaru}.
    We set the number of each kind of node to $12$, thus having 72 processors in total.  % the whole cluster.
%
    Each machine has a (normalized) CPU speed and a memory size (in GB), and we list them as (name, speed, memory):
    ($local$, 4, 16) -- very slow machines; ($A1$, 32, 32), ($A2$, 6, 64), ($N1$, 12, 16) -- average machines;
    ($N2$, 8, 8) -- machine with very small memory; and ($C2$, 32, 192) -- {\em luxury} machine with high speed and
    large memory (see Table~\ref{tab:procs}).

    \begin{table}[htb]
        \begin{center}
            \begin{tabular}{c|c|cc}
                \toprule
                Processor  %& Amount
                &  CPU speed   & \multicolumn{2}{c}{Memory size (GB)} \\
                name & (GHz) & {\em default} & {\em mem-constrained} \\
                \midrule
                local                    & 4                    & 16     & 1.6 \\
                A1                      & 32                   & 32     & 3.2 \\
                A2                      & 6                    & 64    & 6.4 \\
                N1                      & 12                   & 16     & 1.6 \\
                N2                      & 8                    & 8      & 0.8\\
                C2                      & 32                   & 192   &  19.2\\
                \bottomrule
            \end{tabular}
        \end{center}
        \caption{Cluster configuration.}
        \label{tab:procs}
    \end{table}

    We also consider a more constrained setting, by varying the cluster configuration. The
     {\em memory-constrained cluster} is consisting of 72 nodes (12 of each kind) as the default cluster,
     but each node has 10 times less memory. Hence,  
     the {\em luxury} machine $C2$ has $19.2$~GB memory in this setting instead of $192$~GB, 
     $A2$ has $6.4$~GB instead, of $64$~GB etc.
    The processor speeds and their relations stay unchanged (see Table~\ref{tab:procs}).

    \subsubsection{Runtime system}

    To simulate the execution of a workflow, we implemented a runtime system.
    It reads the historical data and builds weights for tasks.
    These weights are then treated as the ``truth'' about the execution during the simulation.
    In the case without errors, these values are being sent to the scheduler.
    However, if errors have to be simulated, the runtime system applies a deviation function to the values.
    The deviation function computed a normally distributed deviated value, where the correct value is the mean and the deviation
    is $10\%$.
    This scenario corresponds to the real-life scenarios identified in~\cite{lotaru} and\skug{todo cite someone Jonathan cites}.
